------------------------------
title: "LABOTARIO_BONUS"
author: "JESSICA PAOLA AGUILAR SERVIN"
date: "2023-03-11"
output: html_document
------------------------------------

##############################
LABORATORIO PLOT HOOVER CURVE
##############################

INSTALAR PREVIAMENTE 
install.packages("devtools")
install.packages("devtools", type = "win.binary")
```{r}
library(devtools)
library(EconGeo)
```

generate vectors industrial 

```{r}
ind <- c(0, 10, 10, 30, 50)
pop <- c(10, 15, 20, 25, 30)
```

CHECK VECTOR
```{r}
ind
```

CHECK VECTOR POP
```{r}
pop
```

RUN THE FUNTION (30% de la poblacion produce 50% de los resultados industriales)
```{r}
Hoover.curve (ind, pop)
```

COMPUTE HOOVER GINI
```{r}
Hoover.Gini (ind, pop)
```

-------------------------------------------------------------------------
#################################
LABORTARIO GINI                
#################################

USAGE
GENERATE VECTORS OF INDUSTRIAL COUNT
```{r}
ind <- c(0, 10, 10, 30, 50)
```


RUN THE FUNCTION
```{r}
Gini (ind)
```

GENERATE A REGION-INDUSTRY MATRIX
```{r}
mat = matrix (
  c (0, 1, 0, 0,
     0, 1, 0, 0,
     0, 1, 0, 0,
     0, 1, 0, 1,
     0, 1, 1, 1), ncol = 4, byrow = T)
rownames(mat) <- c ("R1", "R2", "R3", "R4", "R5")
colnames(mat) <- c ("I1", "I2", "I3", "I4")
```

RUN THE FUNCTION
```{r}
Gini (mat)
```

RUN THE FUNCTION BY AGGREGATING ALL INDUSTRIES
```{r}
Gini (rowSums(mat))
```

RUN THE FUNCTION #1 ONLY(igualdad perfecta)
```{r}
Gini (mat[,1])
```

RUN THE FUNCTION #2 ONLY (igualdad perfecta)
```{r}
Gini (mat[,2])
```

RUN THE FUNCTION #3 ONLY (desigualdad perfecta: max Gini = (5-1)/5)
```{r}
Gini (mat[,3])
```

RUN THE FUNCTION #4 ONLY (top 40% produce el 100% de los resultados)
```{r}
Gini (mat[,4])
```

------------------------------------------------------------------
############################
LABORATORIO HOOVER GINI   
############################

USAGE
Hoover.Gini(MAT,POP)

GENERATE VECTORS OF INDUSTRIAL COUNT
```{r}
ind <- c(0, 10, 10, 30, 50)
pop <- c(10, 15, 20, 25, 30)
```

RUN THE FUNCTION
```{r}
Hoover.Gini (ind,pop)
```

GENERATE A REGION-INDUSTRY MATRIX
```{r}
mat = matrix (
  c (0, 10, 0, 0,
     0, 15, 0, 0,
     0, 20, 0, 0,
     0, 25, 0, 1,
     0, 30, 1, 1), ncol = 4, byrow = T)
rownames(mat) <- c ("R1", "R2", "R3", "R4", "R5")
colnames(mat) <- c ("I1", "I2", "I3", "I4")

```

RUN THE FUNCTION
```{r}
Hoover.Gini (mat,pop)
```

RUN THE FUNCTION BY AGGREGATING ALL INDUSTRIES
```{r}
Hoover.Gini (rowSums(mat),pop)
```

RUN THE FUNCTION #1 ONLY
```{r}
Hoover.Gini (mat[,1],pop)
```

RUN THE FUNCTION #2 ONLY (perfectamente proporcional)
```{r}
Hoover.Gini (mat[,2],pop)

```

RUN THE FUNCTION #3 ONLY (30% produce el 100% de la producción)
```{r}
Hoover.Gini (mat[,3], pop)
```

RUN THE FUNCTION #4 ONLY (55% produce el 100% de la producción)
```{r}
Hoover.Gini (mat[,4], pop)
```

--------------------------------------------------------------------------------
##############################
LABORATORIO LOCATIONAL GINI 
##############################

GENERATE REGION- INDUSTRI MATRIX
```{r}
mat = matrix (
  c (100, 0, 0, 0, 0,
     0, 15, 5, 70, 10,
     0, 20, 10, 20, 50,
     0, 25, 30, 5, 40,
     0, 40, 55, 5, 0), ncol = 5, byrow = T)
rownames(mat) <- c ("R1", "R2", "R3", "R4", "R5")
colnames(mat) <- c ("I1", "I2", "I3", "I4", "I5")
```

RUN THE FUNCTION
```{r}
locational.Gini (mat)
```

----------------------------------
##############################
 LOCATIONAL.GINI_CURVE     
##############################

GENERATE A RECION-INDUSTRI MATRIX
```{r}
mat = matrix (
  c (100, 0, 0, 0, 0,
     0, 15, 5, 70, 10,
     0, 20, 10, 20, 50,
     0, 25, 30, 5, 40,
     0, 40, 55, 5, 0), ncol = 5, byrow = T)
rownames(mat) <- c ("R1", "R2", "R3", "R4", "R5")
colnames(mat) <- c ("I1", "I2", "I3", "I4", "I5")
```


RUN THE FUNCTION (SHOWS INDUSTRY #5)
```{r}
locational.Gini.curve (mat)
locational.Gini.curve (mat, pdf = TRUE)
```

-------------------------------------------------------------

#################################
LABORATORIO LORENZ.CURVE      
#################################

GENERATE VECTORS OF INDUSTRIAL COUNT
```{r}
ind <- c(0, 10, 10, 30, 50)
```


RUN THE FUNCTION
```{r}
Lorenz.curve (ind)
Lorenz.curve (ind, pdf = TRUE)
Lorenz.curve (ind, plot = FALSE)
```

GENERATE A REGION- INDUSTRY MATRIX
```{r}
mat= matrix (
  c (0, 1, 0, 0,
     0, 1, 0, 0,
     0, 1, 0, 0,
     0, 1, 0, 1,
     0, 1, 1, 1), ncol = 4, byrow = T)
rownames(mat) <- c ("R1", "R2", "R3", "R4", "R5")
colnames(mat) <- c ("I1", "I2", "I3", "I4")

```

RUN THE FUNCTION
```{r}
Lorenz.curve (mat)
Lorenz.curve (mat, pdf = TRUE)
Lorenz.curve (mat, plot = FALSE)
```

RUN THE FUNCTION BY AGGREGATION ALL INDUSTRIES
```{r}
Lorenz.curve (rowSums(mat))
Lorenz.curve (rowSums(mat), pdf = TRUE)
Lorenz.curve (rowSums(mat), plot = FALSE)
```


RUN THE FUNCTION FOR INDUSTRIY #1 ONLY (PERFECT EQUALITY)
```{r}
Lorenz.curve (mat[,1])
Lorenz.curve (mat[,1], pdf = TRUE)
Lorenz.curve (mat[,1], plot = FALSE)
```


RUN THE FUNCTION FOR INDUSTRIY #2 ONLY (PERFECT EQUALITY)
```{r}
Lorenz.curve (mat[,2])
Lorenz.curve (mat[,2], pdf = TRUE)
Lorenz.curve (mat[,2], plot = FALSE)
```


RUN THE FUNCTION FOR INDUSTRIY #3 ONLY (PERFECT UNEQUALITY)
```{r}
Lorenz.curve (mat[,3])
Lorenz.curve (mat[,3], pdf = TRUE)
Lorenz.curve (mat[,3], plot = FALSE)
```


RUN THE FUNCTION FOR INDUSTRIY #4 ONLY (PERFECT UNEQUALITY)
```{r}
Lorenz.curve (mat[,4])
Lorenz.curve (mat[,4], pdf = TRUE)
Lorenz.curve (mat[,4], plot = FALSE)
```


COMPARE THE DISTRIBUTION OF THE INDUSTRIES
```{r}
par(mfrow=c(2,2))
Lorenz.curve (mat[,1])
Lorenz.curve (mat[,2])
Lorenz.curve (mat[,3])
Lorenz.curve (mat[,4])
```

